%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Template for Reproduced Sound 2020 
%%% Release 21/09/2020
%%%	Developed by Prof. William D'Andrea Fonseca (Acoustical Engineering, UFSM, Brazil)
%%% will.fonseca@eac.ufsm.br
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Bio page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 150 word biography for each author
\thispagestyle{empty}
\fontsize{10}{12}\selectfont
%% Authors

\textit{Biography:}

\textbf{B. LONG} is a Senior Lecturer in Media Technology with Oxford Brookes University, specialising in audio. He has extensive real world practice of audio engineering, both in music production, sound art installations, and in live and recorded multichannel surround sound productions. He is a member of the Audio Engineering Society, the Institute of Sound and Communications Engineers, and the Institute of Acoustics.  

\textbf{G. G. SMALL} is a Senior Lecturer in Media Technology with Oxford Brookes University, specialising in audio. He has extensive real world practice of audio engineering, both in music production, sound art installations, and in live and recorded multichannel surround sound productions. He is a member of the Audio Engineering Society, the Institute of Sound and Communications Engineers, and the Institute of Acoustics.  

\textbf{R. U. LITTLE} is a Senior Lecturer in Media Technology with Oxford Brookes University, specialising in audio. He has extensive real world practice of audio engineering, both in music production, sound art installations, and in live and recorded multichannel surround sound productions. He is a member of the Audio Engineering Society, the Institute of Sound and Communications Engineers, and the Institute of Acoustics.  


\textbf{M. W. SHORT} is a Senior Lecturer in Media Technology with Oxford Brookes University, specialising in audio. He has extensive real world practice of audio engineering, both in music production, sound art installations, and in live and recorded multichannel surround sound productions. He is a member of the Audio Engineering Society, the Institute of Sound and Communications Engineers, and the Institute of Acoustics.  
%% EOF %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
